Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-06-11 paper/submitted/round2_png/mathematical_formulation_v4_cmame.tex
Minor edits, more to come

We further consider the case of a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI). We denote a scalar QoI by  is a functional that maps the parameters and state to our QoI. We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use. In the following, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations. We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \Cref{eq:invOpt_cons}.
%
%------------------------------------------------------------------------------%
\subsection[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse Problem}  \label{sec:deriv}
%------------------------------------------------------------------------------%
%
For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates. In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
%
\begin{proposition}
\label{thm:error_estimate}
Consider the inverse problem described by the constrained optimization problem \Cref{eq:invOpt}. Let the form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$. Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$. Also, let the regularization operator $R:Q\to\Reals$ be differentiable with respect to the parameter $q$, and the functional $I:Q\times U\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.

>>>>

In a {\em goal-oriented inverse problem}, where the ultimate purpose of inferring the unknown parameters is to calculate some quantity of interest (QoI). We denote a scalar QoI by  is a functional that maps the parameters and state to our QoI, $I:Q \times U \to \R$. The QoI evaluated with the high ($I(q_{HF},u_{HF})$), low ($I(q_{LF},u_{LF})$) or mixed ($I(q_{MF},u_{MF})$) fidelity models correspondingly map parameters and state from the high, low or mixed fidelity function spaces to QoI values. We then consider the tradeoff between the error in the QoI and the fidelity (and corresponding computational expense) of the model we use. In the following, we introduce the QoI functional $I$ into the inverse problem formulation by introducing auxiliary variables and additional adjoint equations. We then use this formulation to derive an a posteriori error estimate for $I$, where the errors considered are those due to the use of different multi-fidelity models in the constraint \Cref{eq:invOpt_cons}.
%
%------------------------------------------------------------------------------%
\subsection[Error Estimate for a Goal-Oriented Inverse Problem]{Error Estimate for a Goal-Oriented Inverse Problem}  \label{sec:deriv}
%------------------------------------------------------------------------------%
%
For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates. In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model.
%
\begin{proposition}
\label{thm:error_estimate}
Consider the inverse problem described by the constrained optimization problem \Cref{eq:invOpt}. Let the form $a:U \times U \to \Reals$ be three times continuously differentiable with respect to the state $u$ and parameters $q$. Let the observation operator $C:U\to\Reals^{n_d}$ be three times continuously differentiable with respect to the state $u$. Also, let the regularization operator $R:Q\to\Reals$ be differentiable with respect to the parameter $q$, and the functional $I:Q\times U\to\Reals$ be differentiable with respect to the state $u$ and parameter $q$.
